---
title: "report"
author: "Martin"
date: "May 11, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```
# Formatting
The first thing we want to do -- after reading in the data -- is formatting. That'll make things consistent and easier for computations & comparisons along the way. 
```{r include=TRUE}
setwd("C:/Users/martDawg/Desktop")
library(ggplot2)
library(plotly)
# read the data
df <- read.csv('homework_example_data.csv', header=TRUE, stringsAsFactors = FALSE)
names(df) <- gsub('.', '', names(df), fixed = TRUE)
# cleaning some column data
df$XNewSessions <- gsub('%', '', df$XNewSessions, fixed = TRUE)
df$EcommerceConversionRate <- gsub('%', '', df$EcommerceConversionRate, fixed=TRUE)
df$BounceRate <- gsub('%', '', df$BounceRate, fixed=TRUE)
df$EcommerceConversionRate <- as.numeric(df$EcommerceConversionRate)
df$XNewSessions <- as.numeric(df$XNewSessions)
df$EcommerceConversionRate <- as.numeric(df$EcommerceConversionRate)
df$BounceRate <- as.numeric(df$BounceRate)
df$Medium <- gsub(' ', '', df$Medium, fixed=TRUE)
# Standardize format of Avg Session Duration
df$AvgSessionDuration <- ifelse(nchar(df$AvgSessionDuration) == 7,
                                df$AvgSessionDuration,
                                substr(df$AvgSessionDuration, 3, nchar(df$AvgSessionDuration)))
# Derive session minutes column
df$AvgSessionMinutes <- as.numeric(substr(df$AvgSessionDuration, 3,4))+ 
    as.numeric(substr(df$AvgSessionDuration, 6,7))/60
```

## The Objective

We want to measure the effectiveness of our marketing campaign. We have some Google Analytics data -- ie Source, Medium, & Converson Rate -- for all our traffic sources. 

```{r echo=FALSE}
library(knitr)
kable(df[1:5,], caption="What we're starting with:")
```

So we'll attempt to ask two questions of this data

1. Is there a relationship between the medium type and transactions, and
2. Are 

### Looking at Transactions
Since our stated primary objective is transactions we'll focus on Mediums that had transactions. 


```{r }
library(plyr)
med <-ddply(df, ~Medium, summarise, tot_transactions = sum(Transactions))
med <-med[order(med$tot_transactions, decreasing=TRUE),]
rownames(med) <- 1:nrow(med)
med_lst <- med[1:12, "Medium"]
barplot(med$tot_transactions, xlab="Medium", ylab = "Total Transactions")
```
#

The number of transactions by Medium follows a negative exponential distribution: Transaction totals decrease precipitously, with the top 3 -- organic, (none), and referral -- making up more than the rest combined. Given the diminishing returns we'll focus on the top 10: `r med_lst`.

```{r }
df2 <- filter(df, Medium %in% med_lst)
ggplot(df2, aes(x=Medium, y=Transactions))+geom_bar(stat="identity")+
  labs(title="Top 12 Mediums for Driving Purchases")
```

With this subset, let's dig deeper into the trasactions. Until now we've only looked at aggregate -- ie total -- transactions. But that's only part of the story: To optimize our marketing dollars we need to know the success rate as well. 

Specifically, we'll look at the relationship between conversion rate and session time for each medium. To make the relationship more clear, we'll remove campaigns with no transactions.

```{r }
trans <- filter(df2, Transactions>0, Medium != "(none)", Medium != "organic")
g<-ggplot(trans, aes(x=EcommerceConversionRate, y=AvgSessionMinutes))+geom_jitter(aes(color=Medium, size=Transactions))+
    labs(title="The Longer the Visit, the Higher the Conversion Rate",
         subtitle="Referrals and email mediums have the longest sessions") +geom_smooth()
g
```
```{r}
ggplot(trans, aes(EcommerceConversionRate, XNewSessions))+geom_jitter(aes(colour=Medium))+
    labs(title="Email & Referrals are Most Successful When Targetted at Return Customers")
```

```{r}
email<- filter(df, Medium == 'email')
ref <- filter(df, Medium == 'referral', AvgSessionMinutes <10)
best_ref_sources <- ref[order(ref$EcommerceConversionRate, decreasing=TRUE),][1:10, c("Source", "EcommerceConversionRate","Medium", "Transactions")]
best_email_sources <- email[order(email$EcommerceConversionRate, decreasing=TRUE),][1:10,c("Source", "EcommerceConversionRate","Medium", "Transactions")]
kable(best_ref_sources, caption="Top Referral Sources")
kable(best_email_sources, caption="Top Email Sources")
```


## Findings & Recommendations

We saw there are clear relationships between the medium used for a campaign and the success rate of a campaign. The amount of time users spend on the site is also a key factor in driving success. 

Some other key findings are

1. Email & Referrals are most effective. 
2. The top email source -- with a minimum 50 transactions -- is Klaviyo 
3. The top referral source -- with a minimum 50 transactions -- is transerainc.com. Couponstock.com and Dealscove.com were similarly successful with conversion rates of 56% & 54%, respectively.


Some obvious recommendations include 

1. Focusing time and money on email and referral campaigns, especially with successful sources like Kaviyo and dealscove.com
2. Email & Referral campaings should be targetted heavilly toward past customers. 





