---
title: "report"
author: "Martin"
date: "May 11, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```
# Formatting
The first thing we want to do -- after reading in the data -- is to format it to make our lives easier later. 
```{r include=TRUE}
setwd("d:/mdertz/Desktop")
library(ggplot2)
library(plotly)
# read the data
df <- read.csv('homework_example_data.csv', header=TRUE, stringsAsFactors = FALSE)
names(df) <- gsub('.', '', names(df), fixed = TRUE)
# cleaning some column data
df$XNewSessions <- gsub('%', '', df$XNewSessions, fixed = TRUE)
df$EcommerceConversionRate <- gsub('%', '', df$EcommerceConversionRate, fixed=TRUE)
df$BounceRate <- gsub('%', '', df$BounceRate, fixed=TRUE)
df$EcommerceConversionRate <- as.numeric(df$EcommerceConversionRate)
df$XNewSessions <- as.numeric(df$XNewSessions)
df$EcommerceConversionRate <- as.numeric(df$EcommerceConversionRate)
df$BounceRate <- as.numeric(df$BounceRate)

```

## The Objective

We want to measure the effectiveness of our marketing campaign. We have some Google Analytics data -- ie Source, Medium, & Converson Rate -- for all our traffic sources. 

```{r echo=FALSE}
library(knitr)
kable(df[1:5,], caption="What we're starting with:")
```

### Looking at Transactions
Since our stated primary objective is transactions we'll focus on Mediums that had transactions. 


```{r echo=FALSE}
library(plyr)
med <-ddply(df, ~Medium, summarise, tot_transactions = sum(Transactions))
med <-med[order(med$tot_transactions, decreasing=TRUE),]
rownames(med) <- 1:nrow(med)
med_lst <- med[1:10, "Medium"]
barplot(med$tot_transactions, xlab="Medium", ylab = "Total Transactions")
```
Medium transactions follow a negative exponential distribution: They decrease precipitously, with the top 3 -- organic, (none), and referral -- making up more than the rest combined. Given the diminishing returns we'll focus on the top 10: `r med_lst`.

```{r }
df2 <- filter(df, Medium %in% med_lst)
ggplot(df2, aes(x=Medium, y=Transactions))+geom_bar(stat="identity")+
  labs(title="Top 10 Mediums for Driving Purchases")
```
With this subset, let's dig deeper into the trasactions. Until now we've only looked at aggregate -- ie total -- transactions. But that's only part of the story: To optimize our marketing dollars we need to know the success rate as well. 

```{r }
ggplot(df2, aes(x=EcommerceConversionRate, y=XNewSessions))+geom_jitter(aes(color=Medium, size=Transactions))
```





